---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nflcolors

<!-- badges: start -->
<!-- badges: end -->

The goal of nflcolors is to provide easy access to NFL team colors and palettes.

## Installation

You can install nflcolors from [GitHub](https://github.com/) with:
```{r  eval=FALSE}
# install.packages("devtools")
devtools::install_github("corysauve/nflcolors")
```

## Basic Usage 

nflcolors has palettes for all 32 teams in the National Football League (NFL). Colors are sourced from primary uniforms and logos. All teams are accessed via their team abbreviation.
```{r team-names}
library(nflcolors)

names(teams)
```
You can create a team palette with `team_colors()`, along with an image of the palette.
```{r team-colors}
kc_palette <- team_colors("KC")
```

You can also select a specific number of colors. 
```{r specific-colors}
kc_palette <- team_colors("KC", 2)
```

## Available Team Palettes

* [**AFC South**](#AFC-South) 
* [**AFC East**](#AFC-East) 
* [**AFC North**](#AFC-North) 
* [**AFC West**](#AFC-West) 
* [**NFC South**](#NFC-South) 
* [**NFC East**](#NFC-East) 
* [**NFC North**](#NFC-North) 
* [**NFC West**](#NFC-West)

<br>

### AFC South
```{r afc-south, out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
print.palette <- function(x, ...) {
  n <- length(x)
  old <- par(mar = c(0.5, 0.5, 0.5, 0.5))
  on.exit(par(old))

  image(1:n, 1, as.matrix(1:n), col = x,
        ylab = "", xaxt = "n", yaxt = "n", bty = "n")

  rect(0, 0.9, n + 1, 1.1, col = rgb(1, 1, 1, 0.8), border = NA)
  text((n + 1) / 2, 1, labels = attr(x, "name"), cex = 2, col = "#32373D")
}

afcsouth <- names(teams[c("TEN", "IND", "HOU", "JAX")])

for (pal in afcsouth){
  print.palette(team_colors(pal))
}
```

<br>

### AFC East 
```{r afc-east, out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
afceast <- names(teams[c("BUF", "MIA", "NE", "NYJ")])

for (pal in afceast){
  print.palette(team_colors(pal))
}
```

<br>

### AFC North
```{r afc-north, out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
afcnorth <- names(teams[c("PIT", "BAL", "CLE", "CIN")])

for (pal in afcnorth){
  print.palette(team_colors(pal))
}
```

<br>

### AFC West
```{r afc-west, out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
afcwest <- names(teams[c("KC", "LV", "LAC", "DEN")])

for (pal in afcwest){
  print.palette(team_colors(pal))
}
```

<br>

### NFC South
```{r nfc-south, out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
nfcsouth <- names(teams[c("NO", "TB", "CAR", "ATL")])

for (pal in nfcsouth){
  print.palette(team_colors(pal))
}
```

<br>

### NFC East
```{r nfc-east, out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
nfceast <- names(teams[c("WAS", "NYG", "DAL", "PHI")])

for (pal in nfceast){
  print.palette(team_colors(pal))
}
```

<br>

### NFC North
```{r nfc-north, out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
nfcnorth <- names(teams[c("GB", "CHI", "MIN", "DET")])

for (pal in nfcnorth){
  print.palette(team_colors(pal))
}
```
 
<br>

### NFC West 
```{r out.width="350px", echo = FALSE, warning = FALSE, message = FALSE}
nfcwest <- names(teams[c("SEA", "LAR", "ARZ", "SF")])

for (pal in nfcwest){
  print.palette(team_colors(pal))
}
```

<br>

## Contributing 

I welcome any contributions or suggestions for improving the package! Please open an issue to do so.

## License 

The nflcolors package is licensed under the MIT License. Please see the [LICENSE](LICENSE.md) for more details.

## Acknowledgments 

Inspiration for this package originally came from the wonderful [nationalparkcolors](https://github.com/katiejolly/nationalparkcolors) package, which provides color palettes for various National Park posters.

