---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nflcolors

<!-- badges: start -->
<!-- badges: end -->

The goal of nflcolors is to provide 

## Installation

You can install nflcolors from [GitHub](https://github.com/) with:

```{r  eval=FALSE}
# install.packages("devtools")
devtools::install_github("corysauve/nflcolors")
```
## Basic Usage 

`nflcolors` has palettes for all 32 teams in the National Football League (NFL). Colors are sourced from primary uniforms and logos. All teams are accessed via their team abbreviation.
```{r team-names}
library(nflcolors)

names(teams)
```
You can create a team palette with `team_colors()`, along with an image of the palette.
```{r team-colors}
kc_palette <- team_colors("KC")
```

You can also select a specific number of colors. 
```{r specific-colors}
kc_palette <- team_colors("KC", 2)
```


## Available Palettes 
```{r out.width="300px", echo = FALSE, warning = FALSE, message = FALSE}
print.palette <- function(x, ...) {
  n <- length(x)
  old <- par(mar = c(0.5, 0.5, 0.5, 0.5))
  on.exit(par(old))

  image(1:n, 1, as.matrix(1:n), col = x,
        ylab = "", xaxt = "n", yaxt = "n", bty = "n")

  rect(0, 0.9, n + 1, 1.1, col = rgb(1, 1, 1, 0.8), border = NA)
  text((n + 1) / 2, 1, labels = attr(x, "name"), cex = 1, col = "#32373D")
}

pals <- names(teams)
for (pal in pals){
  print.palette(team_colors(pal))
}
```
